Title here

### 2020-09-02 paper/paper.Rmd
more changes of the section title, add new section on animated plots
spelling
apply the botanical palette to plot construction

p1 <- dt %>% explore_trace_search() + 
  ggtitle("satisfactory")

p2 <- holes_2d_better %>% explore_trace_search() + 
  ggtitle("not satisfactory")

@@

## Examining the interpolation progress

@@

```{r toy-interp, fig.height = 8, fig.cap = "\\label{toy-interp} This is a toy example of plotting interpolated points"}
interp <- holes_2d_better_max_tries %>% 
  filter(info == "interpolation") %>% 
  mutate(id = row_number())

p1 <- interp %>% 
  ggplot(aes(x = id, y = index_val, col = as.factor(tries))) + 
  geom_point() + 
  geom_line() + 
  theme(legend.position = "bottom") + 
  ggtitle("satisfactory")

p2 <- interrupt_no %>% explore_trace_interp() + 
  theme(legend.position = "bottom") + 
  ggtitle("not satisfactory")

p3 <- holes_2d_better_random %>% explore_trace_interp() + 
  theme(legend.position = "bottom") + 
  ggtitle("maybe satisfactory?")

@@

### Understanding the optimiser's coverage of the search space

@@

#####
dt <- bind_rows(holes_2d_better %>% mutate(algo = "not satisfactory"), holes_2d_better_max_tries %>% mutate(algo = "satisfactory")) %>% mutate(info = ifelse(info == "start", "new_basis", info)) %>% 
  compute_pca() %>% 
  `$`(combined)

last <- dt %>% 
  filter(info == "interpolation") %>% 
  group_by(algo) %>% 
  filter(id == max(id))

start <- dt %>% filter(id == 1)

dt %>% filter(!is.na(info)) %>% 
  ggplot() + 
  geom_point(aes(x = PC1, y = PC2, col = info)) + 
  geom_point(data = last, aes(x = PC1, y = PC2, col = info), size = 7) + 
  geom_point(data = start,aes(x = PC1, y = PC2, col = info), size = 7) + 
  facet_wrap(vars(algo)) + 
  theme(aspect.ratio = 1, legend.position = "bottom")

@@

## A more complex example: Choosing the initial value for polishing parameter

>>>>

p1 <- dt %>% explore_trace_search() + 
  ggtitle("satisfactory") + 
  scale_color_botanical(palette = "daisy")

p2 <- holes_2d_better %>% explore_trace_search() + 
  ggtitle("not satisfactory") + 
  scale_color_botanical(palette = "daisy")

@@

## Examining the optimisation progress

@@

```{r toy-interp, fig.height = 8, fig.cap = "\\label{toy-interp} This is a toy example of plotting interpolated points"}
p1 <- holes_2d_better_max_tries %>% explore_trace_interp() + theme(legend.position = "none") + 
  scale_color_botanical(palette = "fern_brown")

p2 <- interrupt_no %>% explore_trace_interp() + theme(legend.position = "none") + 
  scale_color_botanical(palette = "fern_green")

p3 <- holes_2d_better_random %>% explore_trace_interp() + theme(legend.position = "none") + 
  scale_color_botanical(palette = "acacia")

@@

## Understanding the optimiser's coverage of the search space

@@

#####
# theory <- matrix(c(0,0, 1,0,0,0, 0, 1, 0, 0,0,0), ncol = 2)
# index <- holes()
# index(as.matrix(data_mult) %*% theory)
# 
# 
# theory <-orthonormalise(matrix(c(0,0.2, 0.7,0,0,0, 0, 0.7, 0.2, 0,0,0), ncol = 2))
# theory 
# index <- holes()
# index(as.matrix(data_mult) %*% get_last_basis(holes_2d_better))

dt <- bind_rows(holes_2d_better %>% mutate(algo = "not satisfactory"), holes_2d_better_max_tries %>% mutate(algo = "satisfactory")) %>% mutate(info = ifelse(info == "start", "new_basis", info)) %>% 
  compute_pca() %>% 
  `$`(combined)
last <- dt %>% 
  filter(info == "interpolation") %>% 
  group_by(algo) %>% 
  filter(id == max(id))
start <- dt %>% filter(id == 1)
dt %>% filter(!is.na(info)) %>% 
  ggplot() + 
  geom_point(aes(x = PC1, y = PC2, col = info)) + 
  geom_point(data = last, aes(x = PC1, y = PC2, col = info), size = 7) + 
  geom_point(data = start,aes(x = PC1, y = PC2, col = info), size = 7) + 
  facet_wrap(vars(algo)) + 
  theme(aspect.ratio = 1, legend.position = "bottom")

@@
